### 2019-02-25 ICRA19/covControl.tex
added references to the video

\section{Experiments}\label{sec:Experiments}
This section reviews three demonstrations of efficient shape control of many particles.
\subsection{Hardware experiment: particle angle of repose}
In this section we varied the approach angle to shape a swarm with a characteristic angle of repose.  
We then showed how the angle of repose can be increased by decreasing the magnitude of the force that moves the particles.
%
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{aorPlot.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:angleOfReposeExp}
Experimental data using iron particles, varying angle of attack, and three tilt angles to vary the force applied by gravity (see \cite{shahrokhiICRAvideo2019}).
}\vspace{-1.5em}
\end{figure}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
%\end{center}
%\caption{\label{fig:ironAndSaltCloseup}
%Magnified image of salt and iron at angle of repose.
%}
%\end{figure}
%
The particles used are iron filings (Dowling Magnets, \#731019, $\approx0.5$~mm diameter), and the motive force is gravity as shown in Fig.~\ref{fig:angleOfReposeExp}. 
The particles were poured into a frame composed of two sheets of acrylic with 4.5 mm spacing between. Five 40 mm rods were epoxied between the sheets at angles 
 $\{0^\circ,15^\circ, 30^\circ, 45^\circ, 60^\circ \}$, generating angle of attacks $\beta = \{90^\circ,75^\circ, 60^\circ, 45^\circ, 30^\circ \}$.
 The frame was tested at three tilt angles with respect to horizontal: $\beta = \{90^\circ,60^\circ, 45^\circ \}$, resulting in $\{100,87, 71\}\%$ of the gravitational force.
 For each test the bottom of the frame was removed to allow unsupported particles to escape and the shape of the remaining particles was measured from photographs taken by a tripod-mounted camera inclined at the same tilt angle as the frame.
  The decreasing tilt angles resulted in increasing angle of repose values: $\alpha = \{42^\circ,50^\circ, 63^\circ \}$, corresponding to Fig.~\ref{fig:AngleOfReposeForce}(a).
%%% We removed these because they seemed unnecessary
% These experiments show how the pile of particles can be used to convey two scalar values: the force applied and the attack angle. 
% These result in varying levels of force and torque on the rod according to \eqref{eq:ForceAOR} and \eqref{eq:TorqueAOR}.

\subsection{Hardware experiment: Kilobot angle of repose}
We varied the approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a 3 cm diameter,  low-cost robot. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp} also showing angle of repose of 56 Kilobots with  the pink rod at three angles of attack: 90$^\circ$, 67.5$^\circ$ and 45$^\circ$, generating three different shapes, as in Fig.~\ref{fig:angle}. The green lines show the triangle shape the robots pile up into. The cyan star is the center of mass of the rod, and the mean position and variance of the robots are shown with red stars and red ellipses.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:SetUp}
Steering Kilobots with lights and characteristic shape formed by Kilobot angle of repose for three angle of attacks (see \cite{shahrokhiICRAvideo2019}).
}\vspace{-1.5em}
\end{figure}

>>>>

\section{Experiments}\label{sec:Experiments}
This section reviews three demonstrations of efficient shape control of many particles.
\subsection{Hardware experiment: particle angle of repose}
In this section we varied the approach angle to shape a swarm with a characteristic angle of repose.  
We then showed how the angle of repose can be increased by decreasing the magnitude of the force that moves the particles.
%
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{aorPlot.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:angleOfReposeExp}
Experimental data using iron particles, varying angle of attack, and three tilt angles to vary the force applied by gravity (see video \cite{shahrokhiICRAvideo2019}).
}\vspace{-1.5em}
\end{figure}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{ironAndSaltCloseup.pdf}
%\end{center}
%\caption{\label{fig:ironAndSaltCloseup}
%Magnified image of salt and iron at angle of repose.
%}
%\end{figure}
%
The particles used are iron filings (Dowling Magnets, \#731019, $\approx0.5$~mm diameter), and the motive force is gravity as shown in Fig.~\ref{fig:angleOfReposeExp}. 
The particles were poured into a frame composed of two sheets of acrylic with 4.5 mm spacing between. Five 40 mm rods were epoxied between the sheets at angles 
 $\{0^\circ,15^\circ, 30^\circ, 45^\circ, 60^\circ \}$, generating angle of attacks $\beta = \{90^\circ,75^\circ, 60^\circ, 45^\circ, 30^\circ \}$.
 The frame was tested at three tilt angles with respect to horizontal: $\beta = \{90^\circ,60^\circ, 45^\circ \}$, resulting in $\{100,87, 71\}\%$ of the gravitational force.
 For each test the bottom of the frame was removed to allow unsupported particles to escape and the shape of the remaining particles was measured from photographs taken by a tripod-mounted camera inclined at the same tilt angle as the frame.
  The decreasing tilt angles resulted in increasing angle of repose values: $\alpha = \{42^\circ,50^\circ, 63^\circ \}$, corresponding to Fig.~\ref{fig:AngleOfReposeForce}(a).
%%% We removed these because they seemed unnecessary
% These experiments show how the pile of particles can be used to convey two scalar values: the force applied and the attack angle. 
% These result in varying levels of force and torque on the rod according to \eqref{eq:ForceAOR} and \eqref{eq:TorqueAOR}.

\subsection{Hardware experiment: Kilobot angle of repose}
We varied the approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. 
 A Kilobot is a 3 cm diameter,  low-cost robot. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp} also showing angle of repose of 56 Kilobots with  the pink rod at three angles of attack: 90$^\circ$, 67.5$^\circ$ and 45$^\circ$, generating three different shapes, as in Fig.~\ref{fig:angle}. The green lines show the triangle shape the robots pile up into. The cyan star is the center of mass of the rod, and the mean position and variance of the robots are shown with red stars and red ellipses.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1.5em}
\caption{\label{fig:SetUp}
Steering Kilobots with lights and characteristic shape formed by Kilobot angle of repose for three angle of attacks (see video \cite{shahrokhiICRAvideo2019}).
}\vspace{-1.5em}
\end{figure}

### 2019-02-25 ICRA19/intro.tex
added references to the video

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{firstpic.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:leadfigure} 
     Reshaping particles by collisions with rigid bodies. Top pictures illustrate using closed boundaries to reshape the particles. 
      Bottom pictures illustrate with different particles how varying the the angle of attack modifies the shape of particles remaining on a rigid object and how modifying the applied force changes the angle of repose.
}
\vspace{-1em}
\end{figure}

>>>>

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{firstpic.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:leadfigure} 
     Reshaping particles by collisions with rigid bodies. Top pictures illustrate using closed boundaries to reshape the particles. 
      Bottom pictures illustrate with different particles how varying the the angle of attack modifies the shape of particles remaining on a rigid object and how modifying the applied force changes the angle of repose (see video \cite{shahrokhiICRAvideo2019}).
}
\vspace{-1em}
\end{figure}
